NFC and burnout in teachers - A replication and extension study

### 2022-07-21 Manuscript/Revision_Letter.Rmd
responded to boredom-question

Thank you for this suggestion.
Our intention was not to focus on the significant mediations of Grass et al. (2018), but to deepen the understanding of the role of NFC in burnout.
Therefore, we focussed on RPE, because it is likely the most relevant subscale of the MBI scale in the context of NFC (as Grass et al. also argued).
While Grass et al. (2018) did not find significant correlations between NFC and the subscales DP and EE, Naderi et al. (2018, http://saber.ucv.ve/ojs/index.php/rev_lh/article/view/15958) showed that in students, NFC was significantly correlated with DP and EE, but less so than with RPE.
It has been shown that NFC is positively associated with higher self-efficacy (Rooij et al. (2017), https://doi.org/10.1080/13596748.2017.1381301, and Tan et al. (2020), https://doi.org/10.1007/s12528-019-09239-6), so we also expected NFC to be more strongly associated with the RPE subscale than with DP or EE.
And if the focus in burnout studies with teacher samples has been on the DP and EE subscales, it is all the more reason to focus on the RPE subscale, especially because NFC was equally correlated with all MBI subscales in our teacher sample.
We had preregistered the exploratory analysis of the Demand-Resource-Ratio model with RPE in place of the MBI score, but this model did not have better fit indices than the initial model, which might be attributed to the evenly distributed associations between NFC and the subscales.
Furthermore, when constructing the exploratory model it became clear that NFC was indeed associated with RPE and EE via DRF and DTH, respectively, but the DP subscale did not have any meaningful paths within the model.
Since we have not preregistered any analysis of the association between NFC and DP or EE, and we do not have theory-driven hypotheses regarding these associations,  we do not believe that such analyses would contribute to the goals of the paper.
A change that we will gladly implement is the more specific distinction between the terms "burnout" and "RPE subscale" in the manuscript, thank you for this advice.

@@

\Assignment{Last Author}
\Done

@@

Thank you for addressing this.
We do not consider "being busy" to be the same as "not being bored", because while an employee might have a high workload, the tasks in question might not be interesting or stimulating at all.
In the case of teachers it might be grading essays on a topic they have read about many times, or staying at work until the late evening for parent-teacher conferences.
We looked into the literature on boredom in teachers and found that boredom was one of the main reasons for leaving the job (Tye & O'Brien 2022, https://doi.org/10.1177/003172170208400108), teachers were just as bored during class as their students (Tam et al. 2019, https://doi.org/10.1111/bjep.12309), and teachers have a strong feeling of mission and responsibility but lack the opportunities to implement these priorities (Tuisk 2007, https://doi.org/10.2478/v10099-009-0011-8).

>>>>

Thank you for this suggestion.
Our intention was not to focus on the significant mediations of Grass et al. (2018), but to deepen the understanding of the role of NFC in burnout.
Therefore, we focussed on RPE, because it is likely the most relevant subscale of the MBI scale in the context of NFC (as Grass et al. also argued).
While Grass et al. (2018) did not find significant correlations between NFC and the subscales DP and EE, Naderi et al. (2018, http://saber.ucv.ve/ojs/index.php/rev_lh/article/view/15958) showed that in students, NFC was significantly correlated with DP and EE, but less so than with RPE.
It has been shown that NFC is positively associated with higher self-efficacy (Rooij et al. (2017), https://doi.org/10.1080/13596748.2017.1381301, and Tan et al. (2020), https://doi.org/10.1007/s12528-019-09239-6), so we also expected NFC to be more strongly associated with the RPE subscale than with DP or EE.
And if the focus in burnout studies with teacher samples has been on the DP and EE subscales, it is all the more reason to also focus on the RPE subscale, especially because NFC was equally correlated with all MBI subscales in our teacher sample.
We had preregistered the exploratory analysis of the Demand-Resource-Ratio model with RPE in place of the MBI score, but this model did not have better fit indices than the initial model, which might be attributed to the evenly distributed associations between NFC and the subscales.
Furthermore, when constructing the exploratory model it became clear that NFC was indeed associated with RPE and EE via DRF and DTH, respectively, but the DP subscale did not have any meaningful paths within the model.
Since we have not preregistered any analysis of the association between NFC and DP or EE, and we do not have any theory-driven hypotheses regarding these associations, we do not believe that such analyses would contribute to the goals of the paper.
A change that we will gladly implement is the more specific distinction between the terms "burnout" and "RPE subscale" in the manuscript, thank you for this advice.

@@

@@

Thank you for addressing this.
We do not consider "being busy" to be the same as "not being bored", because while an employee might have a high workload, the tasks in question might not be interesting or stimulating at all.
In the case of teachers it might be grading essays on the same topic they have taught year after year, or staying at work until the late evening for parent-teacher conferences.
We looked into the literature on boredom in teachers, which is unfortunately quite sparse, and found that boredom was one of the main reasons for leaving the job (Tye & O'Brien 2022, https://doi.org/10.1177/003172170208400108), teachers were just as bored during class as their students (Tam et al. 2019, https://doi.org/10.1111/bjep.12309), and teachers have a strong feeling of mission and responsibility but lack the opportunities to implement these priorities (Tuisk 2007, https://doi.org/10.2478/v10099-009-0011-8).
Therefore, we cannot claim that boredom is less prevalent in the teaching profession.
As the distinction between "being busy" and "not being bored" is reflected in the positive correlation between DTH and DTL, we have added a more in-depth discussion of this correlation in the manuscript (see also our response to the fifth comment of Reviewer 3):

> However, the positive association of *demands too high* and *demands too low* in the correlation analysis suggests that boredom and burnout are not mutually exclusive.
A teacher can have a very high workload, which is reflected in an elevated *demands too high* score, but the work in question might not be intellectually stimulating at all or might not appeal to their ideals and goals, which increases their *demands too low* score.
Both of these variables were correlated with higher MBI scores, but in this model, high demands appear to have contributed more to explaining variance in MBI scores than low demands, suggesting that the perceived workload is more important in the burnout context than how stimulating the work is.
